### 2021-06-22 src/paper/report.tex
Add some comments. Add all tex files as pytask dependencies. Fix typo in README on how to propose replacements.

At the core of our agent-based model are physical contacts between heterogeneous agents
(Figure~\ref{fig:model_contacts_infections}).\footnote{A detailed comparison with other
approaches  is relegated to Supplementary Material~\ref{sec:literature_review}. The
model most closely related to ours is described in \citet{Hinch2020}.} Each contact
between an infectious individual and somebody susceptible to the disease bears the risk
of transmitting the virus. Contacts occur in up to four networks: Within the household,
at work, at school, or in other settings (leisure activities, grocery shopping, medical
appointments, etc.). Some contacts recur regularly, others occur at random. Empirical
applications can take the population and household structure from census data and the
network-specific frequencies of contacts from diary data measuring contacts before the
pandemic \citep[e.g.][]{Mossong2008,Hoang2019}. Within each network, contacts are
differentiated by age and geographical location (see
Section~\ref{sub:number_of_contacts} of the Supplementary Material).

@@

    \floatfoot{\noindent \textit{Note:}
        A
        % formal
        description of the model can be found in Supplementary Material~\ref{sec:model}.
        Figure~\ref{fig:model_contacts_infections} shows the influence on an agent's
        contacts to other agents. Demographic characteristics set the baseline number of
        contacts in different networks. She may reduce the number of contacts due to
        NPIs, showing symptoms, or testing positively for SARS-CoV-2. Infections may
        occur when a susceptible agent meets an infectious agent; the probability
        depends on the type of contact, on seasonality, and on NPIs. If infected, the
        infection progresses as depicted in Figure~\ref{fig:model_disease_progression}.
        If rapid tests are avaible, agents' demand is modeled as in
        Figure~\ref{fig:model_rapid_tests}. All pupils are attending school are tested,
        other reasons trigger a test only for a fraction of individuals.
        Figure~\ref{fig:model_official_cases} shows the model of translating all
        infections in the simulated data to age-specific recorded infections. The model
        uses data on the aggregate share of recorded cases, on the share of positive PCR
        tests triggered by symptoms, and on the false positive rate of rapid tests. The
        lower part of the graph is relevant only for periods where rapid tests are
        available.}
\end{figure}

@@

The main issue with official case numbers is that they will contain only a fraction of
all infections. We thus model official cases as depicted in
Figure~\ref{fig:model_official_cases}. We take aggregate estimates of the share of
detected cases and use data on whether CoViD-19 symptoms led to a PCR test. As the share
of asymptomatic individuals varies by age group, this gives us age-specific shares (see
Figure~\ref{fig:share_known_cases_by_age_group} for the share of known cases by age
group over time in our model). Our estimates suggest that---in the absence of rapid
testing---the detection rate is two to three times higher for individuals above age 80
compared to school age children.\comment[id=K]{Must be verified once results are final.}
Once rapid test become available, confirmation of a positive result is another reason
leading to positive PCR tests.

>>>>

At the core of our agent-based model are physical contacts between heterogeneous agents
(Figure~\ref{fig:model_contacts_infections}).\footnote{A detailed comparison with other
approaches  is relegated to Supplementary Material~\ref{sec:literature_review}. The model
most closely related to ours is described in \citet{Hinch2020}.} Each contact between an
infectious individual and somebody susceptible to the disease bears the risk of
transmitting the virus. Contacts occur in up to four networks: Within the household, at
work, at school, or in other settings (leisure activities, grocery shopping, medical
appointments, etc.). Some contacts recur regularly, others occur at random. Empirical
applications can take the population and household structure from census data and the
network-specific frequencies of contacts from diary data measuring contacts before the
pandemic \citep[e.g.][]{Mossong2008,Hoang2019}. Within each network,
\replaced[id=K]{meeting probabilities depend on}{contacts are differentiated by}
age and
geographical location (see Section~\ref{sub:number_of_contacts} of the Supplementary
Material).

@@

    \floatfoot{\noindent \textit{Note:} A        % formal
        description of the model can be found in Supplementary Material~\ref{sec:model}.
        Figure~\ref{fig:model_contacts_infections} shows the influence on an agent's
        contacts to other agents. Demographic characteristics set the baseline number of
        contacts in different networks. She may reduce the number of contacts due to
        NPIs, showing symptoms, or testing positively for SARS-CoV-2. Infections may
        occur when a susceptible agent meets an infectious agent; the probability depends
        on the type of contact, on seasonality, and on NPIs. If infected, the infection
        progresses as depicted in Figure~\ref{fig:model_disease_progression}. If rapid
        tests are available, agents' demand is modeled as in
        Figure~\ref{fig:model_rapid_tests}. \textcolor{blue}{For each reason only a share
        of eligible individuals receive a test. The share of eligible individuals that
        get tested depends on the reason and changes over time (see
        Figure~\ref{fig:rapid_test_demand}).} \textcolor{red}{All pupils are attending
        school are tested, other reasons trigger a test only for a fraction of
        individuals.} Figure~\ref{fig:model_official_cases} shows the model of
        translating all infections in the simulated data to age-specific recorded
        infections. The model uses data on the aggregate share of recorded cases, on the
        share of positive PCR tests triggered by symptoms, \textcolor{red}{and on the
        false positive rate of rapid tests}. The lower part of the graph is relevant only
        for periods where rapid tests are available.}
\end{figure}

@@

The main issue with official case numbers is that they will contain only a fraction of
all infections. We thus model official cases as depicted in
Figure~\ref{fig:model_official_cases}.\comment[id=K]{I don't understand why we mention
the false positive rates in the floatfoot of this. I would either mention rapid test
sensitivity and specificity in general or not mention them at all.} We take aggregate
estimates of the share of detected cases and use data on whether CoViD-19 symptoms led to
a PCR test. As the share of asymptomatic individuals varies by age group, this gives us
age-specific shares (see Figure~\ref{fig:share_known_cases_by_age_group} for the share of
known cases by age group over time in our model). Our estimates suggest that---in the
absence of rapid testing---the detection rate is two to three times higher for
individuals above age 80 compared to school age children.\comment[id=K]{Must be verified
once results are final.} Once rapid test become available, confirmation of a positive
result is another reason leading to positive PCR tests.
